An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-03 poly-embed-journal/poly-embed-journal.tex
Filling in proofs in Appendix E

\jessie{Getting to $\V^*$ through $\H^*$, which exists (and contains $\H_\Y$)}
\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
  Moreover, $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).

@@

\begin{assumption}\label{assum:V-star-exists-infinite}
	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
	$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
	Finally, $\V^* \subseteq \V \subseteq L(\R)$ is the (unique) finite irredundant set such that $g_{L(\R)} = g_\V = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_\V) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, the last of which is irredundant.
\end{assumption}

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V$ and $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	\jessie{TODO}
\end{proof}

@@

\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	%For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
	Then $\cup_{v\in\V^*} \pi(F_v^{\hyp(g_{\V^*})}) = \reals^\Y_+$.
\end{corollary}

@@

\begin{claim}\label{claim:pi-preserves-dim}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
	For all $v \in L(\R)$, define $F_v$ as the face of $g_\V$ generated by $v \in \reals^\Y_+$.
	Then $\dim(F_v) = \dim(\pi(F_v))$.
\end{claim}
\begin{proof}
	\jessiet{Can use a careful check}
	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
	%\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
	Recall from Definition~\ref{def:face} that the dimension of a polytope to be the dimension of its affine hull.
	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
	We claim their projections $\{\pi(z_i)\}$ are affinely independent.
	Let $a_1 + \ldots + a_{|\Y|+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
	We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.

@@

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, fix $x \in \reals^\Y_+$.
	For any $v \in L(\R)$, the following are equivalent:

	(1) $(x,g_\V(x)) \in F_v^{\hyp(g_\V)}$; % H_v \cap \hyp(g_\V)$

	(2) $\inprod{v}{x}= g_\V(x)$;

	(3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$; and

	(4) $x \in \pi(F_v^{\hyp(g_\V)})$~.
\end{lemma}
\begin{proof}
	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
	\begin{align*}
	(1) \quad \quad (x,g(x)) \in F_v
	&\iff (x,g_\V(x)) \in \{(x',c) \in \hyp(g_\V) \mid \inprod{v}{x'} = c\} & \\
	&\iff  \inprod{v}{x} = g_\V(x) & (2)\\
	&\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x} & \\
	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}~. & (3)
	\end{align*}
	This covers $1 \iff 2 \iff 3$.

	For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
	For the reverse implication, consider some $x \in \pi(F_v)$.
	There must be a $c \in \reals$ so that $(x,c) \in F_v$.
	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_\V) \mid \inprod{v}{x'} = c\}$.
	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $\hyp(g_\V)$ at $x$ if any only if $\inprod{v}{x} = g_\V(x)$.
	Therefore, we have $(x, g_\V(x)) \in F_v$.
\end{proof}

Taking $L,\V,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_\V)$, $F_{v^*} = H_{v^*} \cap \hyp(g_\V)$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_\V)}_v = H_v \cap \hyp(g_\V)$.
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*}) = \hyp(g_\V)$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
\end{proof}

\jessie{Translated versions of lemma~\ref{lem:X} statements incoming}
Now we can observe a set of normals $\V'$ generates faces of $g_{\V}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}

\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq L(\R)$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	($\impliedby$)
	Since $\V^* \subseteq \V'$, we immediately have $\cup_{v \in \V^*} \pi(F_v) \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
	Moreover, $\cup_{v \in \V^*} \pi(F_v) = \reals^\Y_+$ by Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, so $\reals^\Y_+ \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
	As $g_\V$ is only finite on $\reals^\Y_+$ by construction, equality follows.
%commented out Mar 11 - Jessie
%	$\hyp(g_\V) = \cap (\H_\Y \cup \H_{\V'})$ if and only if $\hyp(g_\V) = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
%	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap \hyp(g_\V) = F_{v'} \implies x \in \pi(F_{v'})$.
%	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.

@@

We now claim that a set of projected faces $\{F^{\hyp(g_\V)}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
Given $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, denote $\Lambda_{S} := \{\pi(F_v) \mid v \in S\}$ as the set of projected facets generated by $\V^*$.

\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
	%For $\V' \subseteq \V$, 
	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_{\V'}$.
	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
	$\implies$
	The result follows if $\V^* \subseteq \V'$, which follows from the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda_{\V^*} \cap \Lambda_{\V'} = \Lambda_{\V^*}$.
	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

	$\impliedby$
	If $\{\pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \{\pi(F_v) \mid v \in \V^*\} \subseteq \cup_{v \in \V'} \pi(F_v)$.
	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \{\pi(F_v) \mid v \in \V^*\} = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
	The other direction of subset inequality following from $\hyp(g_\V)$ being finite only on $\reals_+^\Y$.	
\end{proof}

@@

\jessie{Not referenced below}
\begin{claim}\label{claim:faces-contained-in-facets}
	Given $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F_v := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet. 
\end{claim}
\begin{proof}
	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
	Moreover, $H^+_v$ is valid, and we have $F_v = H_v \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.

	% subset of facet
	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra as $\hyp(g_\V)$ is a polyhedron.
	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
\end{proof}

\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
\begin{claim}\label{claim:vface-subset-some-vstar-face}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $v \in \V$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though. Old version in comments}
	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.

	It then suffices to show that if $F_v := H_v \cap \hyp(g_\V)$ is a face of the facet $F_y := H_y \cap \hyp(g_\V)$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
	Recall from the definition of a face that $F_v = \hyp(g_\V) \cap H_v$ and $F_y = \hyp(g_\V) \cap H_y$.
	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
	Thus, $F_v \neq F_y$ by unique determination of facets.
	If $F_v$ is not a facet of $\hyp(g_\V)$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_\V)$. 
	In both cases, we have $F_v \neq F_y$, and the result follows.

@@

\begin{corollary}\label{cor:projected-faces-subset-projected-facet}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_\V)$ be a face of $\hyp(g_\V)$.
	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
\end{corollary}

Now, we can conclude that projected facets generated by $\V$ contain all other projected faces of $\hyp(g_\V)$.
\begin{corollary}\label{cor:exists-vstar-projected-face-subset}
	Consider $L, \V, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $v \in L(\R)$, let $F_v := H_v \cap \hyp(g_\V)$ be a face of $\hyp(g_\V)$. 
	For any $v \in \V$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
	\btw{shows (7) on $\reals^\Y_+$}
\end{corollary}
\begin{proof}
	This is exactly Claim~\ref{claim:vface-subset-some-vstar-face} and Corollary~\ref{cor:projected-faces-subset-projected-facet} chained together.
\end{proof}

% \begin{claim}
%   \jessie{This should probably move down to translating for properties since representative sets are at the core, about properties}
%   $\R'$ is a representative set for $L$ if and only if $\V^* \subseteq L(\R')$.
% \end{claim}
% \begin{proof}
%   Fix $v^* \in \V^*$.
%   If $\R'$ is representative, then for any $p \in \simplex$ such that , 
%   As $g$ is $1$-homogeneous and minimizable, for every $v^* \in \V^*$, there must be some $p \in \simplex$ such that $\inprod{v^*}{p} = \inf_v \inprod{v}{x}$.
%   Thus, it suffices to show subset inclusion for any $p \in \simplex$.
%   Moreover, since $\R'$ is representative, there is some $r' \in \R'$ such that $\inprod{L(r')}{p} = \inf_{v} \inprod{v}{x}$.
%   
%   For the reverse implication, $\V^*$ is representative (since $\cup_{v^* \in \V^*} F_{v^*} = \reals_+^\Y$ in Corollary 8\jessie{make reference}), so any set containing $\V^*$ is also representative.
% \end{proof}

>>>>

\jessie{Getting to $\V^*$ through $\H^*$, which exists (and contains $\H_\Y$)}
\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique irredundant $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
  Moreover, $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
  Since $\hyp(g_\V)$ is full-dimensional by Lemma~\ref{lem:G-full-dimensional}, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).

@@

\begin{assumption}\label{assum:V-star-exists-infinite}
	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and the last of these is irredundant.
\end{assumption}

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	\jessie{TODO}
	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
	Equality of the hypographs follows immediately from equailty of the graphs.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}

@@

\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	%For each $v \in \V^*$, let $F_v = F_v^{\hyp(g_{\V^*})}= H_v \cap \hyp(g_{\V^*})$. \jessiet{redundant?}
	Then $\cup_{v\in\V^*} \pi(F_v^{\hyp(g_{\V^*})}) = \reals^\Y_+$.
\end{corollary}

@@

\begin{claim}\label{claim:pi-preserves-dim}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}. %, let $F_v = H_v \cap \hyp(g_\V)$.
	For all $v \in L(\R)$, define $F_v$ as the face of $g_{\V^*}$ generated by $v \in \reals^\Y_+$.
	Then $\dim(F_v) = \dim(\pi(F_v))$.
\end{claim}
\begin{proof}
	\jessiet{Can use a careful check}
	\btw{See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
	%\jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
	Recall from Definition~\ref{def:face} that the dimension of a polytope to be the dimension of its affine hull.
	Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
	We claim their projections $\{\pi(z_i)\}$ are affinely independent.
	Let $a_1 + \ldots + a_{|\Y|+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
	We want to conclude that we must have $a_i = 0$ for all $i$, meaning they are affinely independent.

@@

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, fix $x \in \reals^\Y_+$.
	For any $v \in L(\R)$, the following are equivalent:

	(1) $(x,g_{\V^*}(x)) \in F_v^{\hyp(g_{\V^*})}$; % H_v \cap \hyp(g_\V)$

	(2) $\inprod{v}{x}= g_{\V^*}(x)$;

	(3) $v \in \argmin_{v' \in L(\R)} \inprod{v'}{x}$; and

	(4) $x \in \pi(F_v^{\hyp(g_{\V^*})})$~.
\end{lemma}
\begin{proof}
	For $v \in L(\R)$, define $F_v := F_v^{\hyp(g_\V)}$.
	\begin{align*}
	(1) \quad \quad (x,g_{\V^*}(x)) \in F_v
	&\iff (x,g_{\V^*}(x)) \in \{(x',c) \in \hyp(g_{\V^*}) \mid \inprod{v}{x'} = c\} & \\
	&\iff  \inprod{v}{x} = g_{\V^*}(x) & (2)\\
	&\iff \inprod{v}{x} = \min_{v' \in L(\R)}\inprod{v'}{x} & \\
	&\iff v \in \argmin_{v' \in L(\R)}\inprod{v'}{x}~. & (3)
	\end{align*}
	This covers $1 \iff 2 \iff 3$.

	For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
	For the reverse implication, consider some $x \in \pi(F_v)$.
	There must be a $c \in \reals$ so that $(x,c) \in F_v$.
	Expanding, this is actually saying $(x,c) \in \{(x',c') \in \hyp(g_{\V^*}) \mid \inprod{v}{x'} = c\}$.
	In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $\hyp(g_{\V^*})$ at $x$ if any only if $\inprod{v}{x} = g_{\V^*}(x)$.
	Therefore, we have $(x, g_{\V^*}(x)) \in F_v$.
\end{proof}

Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_{\V^*})}_v = H_v \cap \hyp(g_{\V^*})$.
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
\end{proof}

\jessie{Translated versions of lemma~\ref{lem:X} statements incoming}
Now we can observe a set of normals $\V'$ generates faces of $g_{\V^*}$ whose projections cover $\reals^\Y_+$ if and only if the set contains $\V^*$.
This will translate to a set being representative for a loss if and only if it contains a finite minimum representative set (in settings where one exists.)
%\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
%\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}

\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq L(\R)$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	($\impliedby$)
	Since $\V^* \subseteq \V'$, we immediately have $\cup_{v \in \V^*} \pi(F_v) \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
	Moreover, $\cup_{v \in \V^*} \pi(F_v) = \reals^\Y_+$ by Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, so $\reals^\Y_+ \subseteq \cup_{v' \in \V'} \pi(F_{v'})$.
	As $g_{\V^*}$ is only finite on $\reals^\Y_+$ by construction, equality follows.
%commented out Mar 11 - Jessie
%	$\hyp(g_\V) = \cap (\H_\Y \cup \H_{\V'})$ if and only if $\hyp(g_\V) = \cap \H_{\V'}$ when restricting to $x \in \reals_+^\Y$.
%	This implies that for all $x \in \reals_+^\Y$, there exists a $v' \in \V'$ such that $(x,g(x)) \in H_{v'} \cap \hyp(g_\V) = F_{v'} \implies x \in \pi(F_{v'})$.
%	As this is true for all $x \in \reals_+^\Y$, we have $\cup_{v \in \V'} \pi(F_{v}) = \reals_+^\Y$.

@@

We now claim that a set of projected faces $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{\V^*})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.

\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $\R' \subseteq \R$ with $\V' := L(\R')$. 
	Let $F_v := F^{\hyp(g_{\V^*})}_v$ denote the face of $\hyp(g_{\V^*})$ generated by $v \in L(\R)$.
	%For $\V' \subseteq \V$, 
	We have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda_{\V^*}  \subseteq \Lambda_{\V'}$.
	\btw{$1$-homogeneous version of rep iff $\Theta_{\V^*}$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
	$\implies$
	The result follows if $\V^* \subseteq \V'$, which follows from the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda_{\V^*} \cap \Lambda_{\V'} = \Lambda_{\V^*}$.
	%$\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

	$\impliedby$
	If $\{\pi(F_v) \mid v \in \V^*\} \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \{\pi(F_v) \mid v \in \V^*\} \subseteq \cup_{v \in \V'} \pi(F_v)$.
	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \{\pi(F_v) \mid v \in \V^*\} = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
	The other direction of subset inequality following from $\hyp(g_{\V^*})$ being finite only on $\reals_+^\Y$.	
\end{proof}

@@

%\jessie{Not referenced below}
%\begin{claim}\label{claim:faces-contained-in-facets}
%	Given $L, \V$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, if some $H_v \in \H$ supports $\hyp(g_\V)$, then $F_v := H_{v} \cap \hyp(g_\V)$ is a nonempty face of $\hyp(g_\V)$, and thus a subset of a facet. 
%\end{claim}
%\begin{proof}
%	Since $H_v$ supports $\hyp(g_\V)$, we know that $\hyp(g_\V) \subseteq H_v^+$ and $F$ is not empty.
%	Moreover, $H^+_v$ is valid, and we have $F_v = H_v \cap \hyp(g_\V)$ is a face of $\hyp(g_\V)$ by definition.
%	
%	% subset of facet
%	Moreover, the faces of $\hyp(g_\V)$ are all convex polyhedra as $\hyp(g_\V)$ is a polyhedron.
%	Any face of $\hyp(g_\V)$ is must then be a lower-dimensional face of a facet, and therefore a subset.
%	\btw{Gr\"unbaum Page 35, Section 3.1 statement 7}
%\end{proof}

\btw{Lemmatta for Lemma showing (7) in Lemma \ref{lem:X}}
\begin{claim}\label{claim:vface-subset-some-vstar-face}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For any $v \in L(\R)$, the face $F_{v} \subseteq F_{v^*}$ for some $v^* \in \V^*$. \jessiet{Need to clarify that face of $\hyp(g_\V)$?} %must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
	\jessie{I'm not sure if this is clear, but this is a new approach to the proof that I generally like better. I can clarify if the wording is not clear though. Old version in comments}
	As $\hyp(g_{\V^*})$ is a polyhedron, each of its faces are convex polyhedra, and is also a face of some facet of $\hyp(g_{\V^*})$; these facets are defined by $\V^*$ and $\Y$ via Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.

	It then suffices to show that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
	Recall from the definition of a face that $F_v = \hyp(g_{\V^*}) \cap H_v$ and $F_y = \hyp(g_{\V^*}) \cap H_y$.
	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
	Thus, $F_v \neq F_y$ by unique determination of facets.
	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
	In both cases, we have $F_v \neq F_y$, and the result follows.

@@

\begin{corollary}\label{cor:projected-faces-subset-projected-facet}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, and $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$.
	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. 
\end{corollary}

Now, we can conclude that projected facets generated by $L(\R)$ contain all other projected faces of $\hyp(g_{\V^*})$.
\begin{corollary}\label{cor:exists-vstar-projected-face-subset}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $v \in L(\R)$, let $F_v := H_v \cap \hyp(g_{\V^*})$ be a face of $\hyp(g_{\V^*})$. 
	For any $v \in L(\R)$, there is a $v^* \in \V^*$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
	\btw{shows (7) on $\reals^\Y_+$}
\end{corollary}
\begin{proof}
	This is exactly Claim~\ref{claim:vface-subset-some-vstar-face} and Corollary~\ref{cor:projected-faces-subset-projected-facet} chained together.
\end{proof}
